Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-06-03 ms.tex
while revising...
some very simple updates to affiliations and a duplicate equation label.

\author{
%
Yuka Fujii\altaffilmark{0} \\
%
David S. Spiegel\altaffilmark{1, 2} \\
%
{\bf and some order:} \\
%
Jason Nordhaus\altaffilmark{3} \\
%
Nikku Madhusudhan\altaffilmark{4} \\
%
Mehrdad Mirbabayi\altaffilmark{1} \\
%
Aaron Parsons\altaffilmark{5} \\
%
Tony Mroczkowski\altaffilmark{6} \\
%
Neil Zimmerman\altaffilmark{7}
}

@@

\affil{$^4$Astronomy Department, UC Berkeley}

\affil{$^5$Naval Research Laboratory}

\affil{$^6$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}

@@

The scaling of convected heat flux, $q_c$, is obtained by dividing the time-dependent net planetary luminosity by the surface area of the core region i.e., $4\pi r_c^2$. 
The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
%%%%%%%%%%
\begin{equation}
L \sim 1.4^{-9} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
Therefore, we have
%%%%%%%%%%
\begin{equation}
q_c \sim q_{c, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
%We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.

>>>>

\author{
%
Yuka Fujii\altaffilmark{0} \\
%
David S. Spiegel\altaffilmark{1, 2} \\
%
{\bf and some order:} \\
%
Jason Nordhaus\altaffilmark{3} \\
%
Nikku Madhusudhan\altaffilmark{4} \\
%
Mehrdad Mirbabayi\altaffilmark{1} \\
%
Aaron Parsons\altaffilmark{4} \\
%
Tony Mroczkowski\altaffilmark{5,6} \\
%
Neil Zimmerman\altaffilmark{7}
}

@@

\affil{$^4$Astronomy Department, University of California Berkeley}

\affil{$^5$National Research Council Fellow}

\affil{$^6$Naval Research Laboratory, 4555 Overlook Ave SW, Washington, DC 20375}

\affil{$^7$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}

@@

The scaling of convected heat flux, $q_c$, is obtained by dividing the time-dependent net planetary luminosity by the surface area of the core region i.e., $4\pi r_c^2$. 
The model of luminosity evolution is taken from \citet{burrows_et_al2001} \citep[see also][]{marley2007}, which resulted in:
%%%%%%%%%%
\begin{equation}
L \sim 1.4^{-9} L_\odot \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \, 	
\label{eq:burrowsLum}
\end{equation}
%%%%%%%%%%
Therefore, we have
%%%%%%%%%%
\begin{equation}
q_c \sim q_{c, J} \left( \frac{t}{4.5 \rm~Gyr} \right)^{-1.3} \left( \frac{M_p}{M_J} \right)^{2.64} \left( \frac{r_c}{r_{c,\,J}} \right)^{-2}\, .
\label{eq:burrowsHeatFlux}
\end{equation}
%%%%%%%%%%
%We estimate the convected heat flux by dividing this luminosity by the surface area of the core region, i.e., $4 \pi r_c^2$.
